### 2020-09-23 LaTeX/sections/paper.tex
edits on the last part

\section{Design alternatives and extensions}

@@

We implement a very simple market where orders all have the same volume: 1 token. Traders submit multiple orders to increase volume. To extend orders with a volume field, it must first be determined if the token are non-divisible or divisible (and to what precision). In this case, \texttt{closeMarket()} needs to look at multiple bids to fulfill a single ask (and vice-versa) and declare its trading rules on partial fills. We also simplify the market rules around ties on price: we execute them FIFO (breaking front-running resistance for ties on prices). A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach is also contingent on the divisibility of tokens. Consider the following corner-case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price. There is not good option: (1) the bids could all be dropped (fair but not market efficient), (2) bids could be prioritized based on time as in \cm (front-running is viable, but in this corner case only), or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}); blockchain `randomness' is generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs} and counter-measures could take a few blocks to select~\cite{boneh2018verifiable}).

\subsection{Cancelations}

\cm does not support trade cancelations. We intend to open and close markets quickly (on the order of blocks), so orders are relatively short-lived. Support for cancelation also opens the market to new front-running issues where other traders (or miners) can displace cancelations until after the market closes (however one benefit of a call market is that beating a cancelation with a new order has no effect, assuming the cancelation is run any time before the market closes). Finally, cancelations have a performance impact. Canceled orders can be removed from the underlying data structure   or accumulated in a list that is cross-checked when closing the market. Removing orders requires a more verbose structure than a priority queue (\eg a binary search tree instead of a heap; or methods to traverse a linked list rather than only pulling from the head). While client software could help point out where the trade is in the data structure, the orderbook can change between submitting the cancelation request and running the method. A linked list with mapping that returns the key for each submitted order seems to be the most tenable data structure.

\subsection{Market clearing price}

Call markets are heralded for fair price discovery. This is why many exchanges use a call market at the end of the day to determine the closing price of an asset, which is an important price both optically (it is well-published) and operationally (many derivates settle based on the closing price). We purposely do not compute a `market clearing price' with \cm because miners can easily manipulate the price (\ie include a single wash trade at the price they want fixed), although they forgo profit for doing so. This is not merely hypothetical---Uniswap (the prominant quote-drive, on-chain exchange) prices have been manipulated to exploit other DeFi applications relying on them. Countermeasures to protect Uniswap price integrity could also apply to \cm: (1) taking a rolling mediant of prices over time, and (2) using it alongside other sources for the same price and forming a consensus. While \cm does not emit a market clearing price, it can be computed by a webapp examining the orderbook at market close.

\subsection{Scheduling events}

As a simple module, \cm is a one-shot market. However it can be extended to re-open with a clean orderbook after \texttt{closeMarket()} is run. Modifiers can enforce when the market operates openly (collecting orders) and when close can be run. In the Princeton paper~\cite{clark2014decentralizing}, the call market is envisioned to run as an alt-coin, where orders accumulate within a block and a miner closes the market as part of the logic of producing a new block (\ie within the same portion of code as computing their coinbase transaction in Bitcoin or Gas Used in Ethereum).

@@

\subsection{Who pays to close/reopen the market?}

It is unlikely that a mining software will become aware of specific DApps, but miners are paid all price improvements in the market and so it is possible that running \texttt{closeMarket()} would pay for itself. However we consider two other (more realistic) scenarios. One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time (until the order book is empty). Once the time window for submitting orders is past, a new market is created (without settling the previous market). Every orders to the new market is also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market. This solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second related issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).

The second solution is to levy a carefully computed fee against the traders for every new order they submit. The fees are accumulated by the DApp to use as a bounty. When the time window for the open market elapses, the user who calls \texttt{closeMarket()} receives the bounty. This is a better solution, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost. However an interest third party (such as the token issuer for a given market) might bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading. If the contract can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}).

@@

\subsection{Off-chain closing}
\label{sec:rollups}

@@

In our \cm variant with rollups, the token issuer is does all the computation (both enqueuing and dequeuing). Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}). Recall that on-chain, such a priory queue can only match 38 pairs at a cost of 5,372,679 gas. With roll-ups, 38 pairs cost 38,863 gas. As the pairs increase, the cost is essentially constant (\eg 1000 pairs cost 38,851 as opposed to 457,326,935 on-chain). Submitting an order costs 39,169 gas on average as opposed to 207,932 on-chain.

>>>>

\section{Design Alternatives and Extensions}

@@

We implement a very simple market where orders all have the same volume: 1 token. Traders submit multiple orders to increase volume. To extend orders with a volume field, it must first be determined if the token is non-divisible or divisible (and to what precision). In this case, \texttt{closeMarket()} needs to look at multiple bids to fulfill a single ask (and vice-versa) and declare its trading rules on partial fills. We also simplify the market rules around ties on price: we execute them in a FIFO manner (breaking front-running resistance for ties on prices). A common trading rule (that does resist front-running) is to fill ties in proportion to their volume (\ie \textit{pro rata} allocation)\footnote{If Alice and Bob bid the same price for 100 tokens and 20 tokens respectively, and there are only 60 tokens left in marketable asks, Alice receives 50 and Bob 10.} however this approach is also contingent on the divisibility of tokens. Consider the following corner-case: 3 equally priced bids of 1 non-divisible token and 1 ask at the same price. There is no good option: (1) the bids could all be dropped (fair but not market efficient), (2) bids could be prioritized based on time as in \cm (front-running is viable, but in this corner case only), or (3) the bid could be randomly chosen (\cf Libra~\cite{mavroudis2019libra}); blockchain `randomness' is generally deterministic and manipulatable by miners~\cite{bonneau2015random,buenz2017proofs} and counter-measures could take a few blocks to select~\cite{boneh2018verifiable}).

\subsection{Cancellations}

\cm does not support order cancelations. We intend to open and close markets quickly (on the order of blocks), so orders are relatively short-lived. Support for cancellation also opens the market to new front-running issues where other traders (or miners) can displace cancellations until after the market closes (however one benefit of a call market is that beating a cancellation with a new order has no effect, assuming the cancellation is run any time before the market closes). Finally, cancellations have a performance impact. Cancelled orders can be removed from the underlying data structure   or accumulated in a list that is cross-checked when closing the market. Removing orders requires a more verbose structure than a priority queue (\eg a binary search tree instead of a heap; or methods to traverse a linked list rather than only pulling from the head). While client software could help point out where the order is in the data structure, the order book can change between submitting the cancellation request and running the method. A linked list with mapping that returns the key for each submitted order seems to be the most tenable data structure.

\subsection{Market Clearing Price}

Call markets are heralded for fair price discovery. This is why many exchanges use a call market at the end of the day to determine the closing price of an asset, which is an important price both optically (it is well-published) and operationally (many derivates settle based on the closing price). We purposely do not compute a `market clearing price' with \cm because miners can easily manipulate the price (\ie include a single wash trade at the price they want fixed), although they forgo profit for doing so. This is not merely hypothetical---Uniswap (the prominent quote-drive, on-chain exchange) prices have been manipulated to exploit other DeFi applications relying on them. Countermeasures to protect Uniswap price integrity could also apply to \cm: (1) taking a rolling mediant of prices over time, and (2) using it alongside other sources for the same price and forming a consensus. While \cm does not emit a market clearing price, it can be computed by a web application examining the order book at market close.

\subsection{Scheduling Events}

As a simple module, \cm is a one-shot market. However it can be extended to re-open with a clean order book after \texttt{closeMarket()} is run. Modifiers can enforce when the market operates openly (collecting orders) and when close can be run. In the Princeton paper~\cite{clark2014decentralizing}, the call market is envisioned to run as an alt-coin, where orders accumulate within a block and a miner closes the market as part of the logic of producing a new block (\ie within the same portion of code as computing their coinbase transaction in Bitcoin or gasUsed in Ethereum).

@@

\subsection{Who Pays to Close/Reopen the Market?}

It is unlikely that a mining software will become aware of specific DApps, but miners are paid all price improvements in the market and so it is possible that running \texttt{closeMarket()} would pay for itself. However we consider two other (more realistic) scenarios. One solution requires a modified closing function, \texttt{closeMarket(n)}, that only processes $n$ orders at a time (until the order book is empty). Once the time window for submitting orders is past, a new market is created (without settling the previous market). Every order submission on the new market also requires to run, say, \texttt{closeMarket(10)} on the older market, thus progressively closing the previous market while accepting orders to the new market. This solution pattern has two issues: first, amortizing the cost of closing the market amongst the early traders of the new market is an added incentive to not submit orders early to the market; the second related issue is if not enough traders submit orders in the new market, the old market never closes (resulting in a backlog of old markets waiting to close).

The second solution is to levy a carefully computed fee against the traders for every new order they submit. The fees are accumulated by the DApp to use as a bounty. When the time window for the open market elapses, the user who calls \texttt{closeMarket()} receives the bounty. This is a better solution, although not perfect: \texttt{closeMarket()} cost does not follow a tight linear increase with the number of orders, and gas prices vary over time which could render the bounty insufficient for offsetting the \texttt{closeMarket()} cost. However an interested third party (such as the token issuer for a given market) might bailout the market when it halts on \texttt{closeMarket()} to facilitate further trading. If the contract can pay for its own functions, an interested party can also arrange for a commercial service (\eg any.sender\footnote{\url{https://github.com/PISAresearch/docs.any.sender}}) to relay the \texttt{closeMarket()} function call on Ethereum (an approach called \textit{meta-transactions}).

@@

\subsection{Off-chain Closing}
\label{sec:rollups}

@@

In our \cm variant with rollups, the token issuer does all the computation (both enqueuing and dequeuing). Thus we switch the priority queue to use a heap with dynamic array, which balances the expense of both operations (instead of optimizing for dequeuing in \texttt{closeMarket()}). Recall that on-chain, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. With roll-ups, 38 pairs cost 38,863 gas. As the pairs increase, the cost is essentially constant (\eg 1000 pairs cost 38,851 as opposed to 457,326,935 on-chain). Submitting an order costs 39,169 gas on average as opposed to 207,932 on-chain.
